\documentclass[letterpaper, titlepage,openright, oneside,11pt]{book}
 %\documentclass[letterpaper,onepage,openright,titlepage,openany,oneside,11pt]{book}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[spanish]{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{dsfont} % colocar los numeros r
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{anysize}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{titlesec}
\usepackage{enumerate}
\usepackage{verbatim}
%%%%%%%%%%%%%%%%%%%%
%\cxset{style7}
%Options: Sonny, Lenny, Glenn, Conny, Rejne, Bjarne, Bjornstrup
%\usepackage[Bjornstrup]{fncychap}

%%%%%%%%%

%pruebas




%%%%%%%%%%
\marginsize {3.8cm}{3.5cm}{4cm}{1.6cm}
\setlength{\paperheight}{24cm} \setlength{\paperwidth}{18cm}
\newtheorem{thm}{Teorema}[section]
\newtheorem{cor}[thm]{Corolario}
\newtheorem{defn}[thm]{Definici\'{o}n}
\newtheorem{ej}[thm]{Ejemplo}
\newtheorem{lem}[thm]{Lema}
\newtheorem{prop}[thm]{Proposici\'{o}n}
\def\bibname{Referencias}
\renewcommand{\contentsname}{Contenido}
\renewcommand{\baselinestretch}{1.1} 
 \renewcommand{\labelenumi}{\Roman{enumi}.} %interlineado
\def\chaptername{Cap\'{\i}tulo }
\decimalpoint

\bibliographystyle{apalike}
\begin{document}
%\input{Portada_principal.tex}
\renewcommand{\tablename}{Tabla}
\frontmatter
\thispagestyle{empty}
%\title{\bf Confiabilidad y algunas pol\'iticas de inventario en transformadores de instrumento.}
%\author{Maldonado Santiago Alma Delia}
%\maketitle
 %\newpage{\pagestyle{empty}
% \cleardoublepage} 

\input{dedic.tex}
\input{agrad.tex}
\tableofcontents
\newpage
\pagestyle{fancy}
\fancyhf{} % delete current setting for header and footer
\fancyhead[LE,RO]{\bfseries\thepage}
%
\fancyhead[LO]{\bfseries\rightmark}%
\fancyhead[RO,LE]{\thepage} % Nœmeros de p‡gina en las esquinas de los encabezados


\mainmatter
\input{introduccion.tex}
\input{generales.tex} 
\input{confia.tex}
\input{aplicacion.tex}
%\input{uutilidad2.tex}
\input{UtilidadFinal.tex}
\input{conclusiones1.tex}
%\input{apen.tex}


\begin{thebibliography}{99}

\bibitem{riesgo} Peter M. Lee. \textbf{``Bayesian 
Statistics an introduction''}. A member of the Hodder Headline Group LONDON (2004). \label{PL}

\bibitem{riesgo} William Q. Meeker and Luis A. Escobar. \textbf{``Statistical Metohds for Reliability Data''}. Wiley series in Probability and Mathematical Statistic (1998). \label{me}

\bibitem{Grandell} Michael S. Hamada Alyson G. Wilson, C. Shane Reese Harry F. Martz \textbf{``Bayesian Reliability''}. Springer-Science+Bisiness (2008).\label{BR}

\bibitem{Grandell} J.F. Lawless \textbf{``Statistical models and methods for lifetime data''}. Wiley series in Probability and Mathematical Statistic (1982).\label{law}


\bibitem{mi} Ming-Hui Chen, Qi-Man Shao and Joseph G. Ibrahim. textbf{``Monte Carlo Methods in Bayesian Computation''}.
Springer-Verlag (2000).\label{mi}


\bibitem{mi} J. M. Bernardo and A. F. M. Smith \textbf{``Bayesian Theory''}.
Wiley series in probability and mathematical statistic (1994).\label{BT}

\bibitem{mi} R Develepment Core Team(2010). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. ISBM 3-900051-070, URL \textbf{\verb"http//www.R-project.org".}\label{r}

\bibitem{gibbs} George Casella; Edward 
I. George \textbf{``Explaining the Gibbs Sampler''}.
The American Statistician  \&  Vol. 46, No. 3. (Aug ., 1992), pp. 167-174.  World Scientific (2000).\label{gibbs}

\bibitem{gibbs} David B. Hitchcock \textbf{``A History of the Metropolis-Hastings Algorithm''}.
The American Statistician  \&  Vol. 57, No. 4. (Nov., 2003), pp. 254-257.  \label{MH}


\bibitem{gibbs} Siddhartha Chib; Edward Greenberg \textbf{``Understanding the Metropolis-Hastings Algorithm''}.
The American Statistician  \&  Vol. 49, No. 4. (Nov., 1995), pp. 327-335.  \label{UMH}

\bibitem{gibbs} Norman L. Johson; Samuel Kotz; N. Balakrishnan \textbf{``Continuous Univariate Distribution''}.Volume 1. Second edition
Wiley series in probability and mathematical statistic (1994).  \label{distribuciones}

\bibitem{f} Geman, S. and D. Geman. \textbf{``Gibbs distribution and Bayesian restoration of images''} . Stochastic relaxation. IEE Transactions on Pattern Analysis and Machine Intelligence 6. (1984), pp 721-741.\label{geman}
\end{thebibliography}
\end{document}
 
 
 
 
